\boldmath Heavy resonances at energy frontier colliders

### 2019-01-31 paper.tex
Updates from ShareLaTeX

\newcommand{\amc}{{\sc MadGraph5\textunderscore}a{\sc MC@NLO}}
\newcommand{\py}{{\sc Pythia8}}
\newcommand{\delphes}{{\sc Delphes3}}

@@

% /eos/experiment/fcc/helhc/utils/delphescards/helhc_v01/card.tcl
% /eos/experiment/fcc/hh/utils/delphescards/fcc_v02/muonMomentumResolutionVsP.tcl
Monte Carlo~(MC) simulated event samples were used to simulate the response of the detector to signal and backgrounds. Signals are generated with \py~\cite{Sjostrand:2014zea} using the leading order cross-section from the generator.
All lepton flavour decays of the $\ZpSSM$ are generated assuming universality of the couplings.\CH{do we need this here? That's too little information, we need a more complete description of all the various processes.}
The SM backgrounds are Drell-Yan, di-jet (QCD), top pairs (\ttbar), $VV$ and \vj\ where $V=W/Z$,  were generated using \amc~\cite{Alwall:2014hca} at leading order only. A k-factor of 2 is applied to all the background processes to account for higher order corrections.
Independent samples have been generated for the training of object tagger described in section~\ref{subsec:mvatagger}.

%{\scshape Pythia} independent samples have been produced for Multi-Variate taggers training (section~\ref{subsec:mvatagger}). QCD has been produced to avoid useless events thanks to a filtering chosen to ensure to have consistent leading jet $\pT$ as the signals considered (pTHatMin = 2500, bias2Selection = on, bias2SelectionPow = 6).\newline
%Tables~\ref{tab:MCtable_bkgd} and ~\ref{tab:MCtable_sig} are summarising all the background and signal samples produced for the various analysis presented in this document.

%\begin{table}[!htb]\centering
%\begin{tabular}{|c|c|c|c|}
%\hline
%\hline
%process & Ngen & generator & k-factor \\
%\hline
%pp\_$ee$\_5f\_HT & $\sim$5M & $mg+p8$ & 2 \\
%pp\_$\mu\mu$\_5f\_HT & $\sim$5M & $mg+p8$ & 2 \\
%pp\_$\tau\tau$\_5f\_HT & $\sim$5M & $mg+p8$ & 2 \\
%pp\_$jj$\_5f\_HT ($j$ = $u$, $d$, $c$, $s$ or $b$) & $\sim$5M & $mg+p8$ & 2 \\
%pp\_$tt$\_5f\_HT & $\sim$5M & $mg+p8$ & 2 \\
%pp\_$Vj$\_5f\_HT ($V$ = $W$ or $Z$ and $j$ = $u$, $d$, $c$, $s$ or $b$) & $\sim$5M & $mg+p8$ & 2 \\
%pp\_$VV$\_5f\_HT ($V$ = $W$ or $Z$) & $\sim$5M & $mg+p8$ & 2 \\
%\hline
%\hline
%\end{tabular}
%\caption{Summary of generated background samples. The following HT (scalar sum of all visible paticles momentum at generator level) binnings have been used : [500, 1000], [1000, 2000], [2000, 5000], [5000, 10000], [10000, 27000], and [27000, 100000] GeV. 5f stands for flavour quaks : u, d, c ,s  and b.}
%\label{tab:MCtable_bkgd}
%\end{table}

%\begin{table}[!htb]\centering
%\begin{tabular}{|c|c|c|c|}
%\hline
%\hline
%process & Ngen & generator & k-factor \\
%\hline
%pp\_$Z'_{SSM}$\_$ll$ ($l$ = $e$, $\mu$ or $\tau$) & \multirow{2}{*}{$\sim$1M} & \multirow{2}{*}{$p8$} & \multirow{2}{*}{1} \\
%mass : \{2,4,5,6,8,10,12,14,15,16,18,20,25,30,35,40,45,50\} TeV & & & \\
%\hline
%pp\_$Z'_{flavano}$\_$\mu\mu$\_5f & \multirow{2}{*}{$\sim$1M} & \multirow{2}{*}{$mg+p8$} & \multirow{2}{*}{1} \\
%mass : \{4,6,8,10,12,14,15,16,18,20,25,30,35,40,45\} TeV & & & \\
%\hline
%pp\_$LQ$\_$\mu\mu$\_5f & \multirow{2}{*}{$\sim$1M} & \multirow{2}{*}{$mg+p8$} & \multirow{2}{*}{1} \\
%mass : \{4,6,8,10,12,14,16,18,20,22,24,26,28,30,32,34,36,38,40\} TeV & & & \\
%\hline
%pp\_$Z'_{TC2}$\_$tt$ & \multirow{2}{*}{$\sim$1M} & \multirow{2}{*}{$p8$} & \multirow{2}{*}{1} \\
%mass : \{2,5,10,15,20,25,30,35\} TeV & & & \\
%\hline
%pp\_$RSG$\_$WW$ & \multirow{2}{*}{$\sim$1M} & \multirow{2}{*}{$p8$} & \multirow{2}{*}{1} \\
%mass : \{2,5,10,15,20,25,30,35\} TeV & & & \\
%\hline
%pp\_$Q^*$\_$qq$ ($q$ = $u$, $d$, $c$, $s$, $b$ or $t$) & \multirow{2}{*}{$\sim$0.6M} & \multirow{2}{*}{$p8$} & \multirow{2}{*}{1} \\
%mass : \{15,20,25,30,35,40,45,50\} TeV & & & \\
%\hline
%pp\_$Z'_{SSM}$\_$jj$ ($j$ = $u$, $d$, $c$, $s$ or $b$) & \multirow{2}{*}{$\sim$1.2M} & \multirow{2}{*}{$p8$} & \multirow{2}{*}{1} \\
%mass : \{10,15,20,25,30,35,40,45,50\} TeV & & & \\
%\hline
%\hline
%\end{tabular}
%\caption{Summary of generated signal samples.}
%\label{tab:MCtable_sig}
%\end{table}

@@

\begin{equation}
E_{F}(n,\alpha) =  \sum \limits_{\frac{n-1}{5}\alpha < \Delta R(k,jet)< \frac{n}{5}\alpha} \ptSup{(k)} \Biggm/ \sum \limits_{\Delta R(k,jet)< \alpha} \ptSup{(k)}
\end{equation}
with $k$ running over the jet constituents and $\alpha=0.05$. We construct 5 variables $E_{F}(n,\alpha)$ with $n=[1,2,3,4,5]$ and use them as input to the BDT.
The $W$ tagging performance has significantly better performance due to the use of the energy-flow variables. We choose the working points for the analyses presented later with a top and $W$ tagging efficiencies of $\epsilon_S^{\text{top}}=60\%$ and $\epsilon_S^{\text{W}}=90\%$ corresponding respectively to a background rejection of $\epsilon_B^{\text{top}}=\epsilon_B^{\text{W}}=90\%$. These working points corresponds to a cut at 0.15 on the BDT value for both taggers. More details can be found in Appendix~\ref{sec:app:mva}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Statistical analysis}
Hypothesis testing is performed using a modified frequentist method based on a profile likelihood that takes into account the systematic uncertainties as nuisance parameters that are fitted to the expected Monte-Carlo. The full shape information is used, which help from the sidebands to reduce the effect of systematics uncertainties in the signal region.
\CH{Still need to add more informations}

@@

%Models with extended gauge groups often feature additional U(1) symmetries with corresponding heavy spin-1 bosons. These bosons, generally referred to as $\Zp$, would manifest themselves as a narrow resonance in the dilepton mass spectrum. Among these models are those inspired by Grand Unified Theories, motivated by gauge unification or a restoration of the left-right symmetry violated by the weak interaction. Examples include the $\Zp$ bosons of the E6 motivated theories~\cite{London:1986jz,Joglekar:2016yap,Langacker:2008yv,Hewett:1988xc} and Minimal models~\cite{Salvioni:2009mt}. The Sequential Standard Model (SSM)~\cite{Langacker:2008yv} posits a $\ZpSSM$ boson with couplings to fermions that are identical to those of the Standard Model $\Z$ boson.\CH{This we have already in the introduction, I think we can remove}

@@

>>>>

\newcommand{\amc}{{\sc MadGraph5\textunderscore}a{\sc MC@NLO}}
\newcommand*{\MGAMC}{\textsc{MG5}\_aMC}

\newcommand{\py}{{\sc Pythia8}}
\newcommand{\delphes}{{\sc Delphes3}}
\newcommand*{\pdf}[1]{\texttt{#1}}

@@

Monte Carlo~(MC) simulated event samples are used to simulate the response of the detector to signal and backgrounds. Signals are generated with \py~\cite{Sjostrand:2014zea} version v8.201 with the \pdf{NNPDF2\!.\!3NNLO} PDF set~\cite{Ball:2014uwa} using the leading order cross-section from the generator with no k-factor. 
The SM backgrounds are Drell-Yan, di-jet (QCD), top pairs (\ttbar), $VV$ and \vj\ where $V=W/Z$,  were generated using \MGAMC~\cite{Alwall:2014hca} v2.3.3 at leading order only with the XXX PDF set in bins of $\hht$. A k-factor of 2 is applied to all the background processes to account for higher order corrections.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Statistical analysis}
Hypothesis testing is performed using a modified frequentist method based on a profile likelihood that takes into account the systematic uncertainties as nuisance parameters that are fitted to the expected Monte-Carlo. The full shape information is used, which help from the sidebands to reduce the effect of systematics uncertainties in the signal region. The test statistic $q_\mu$ is defined as the profile log-likelihood ratio:
$q_\mu = -2\ln({\cal L}(\mu,\hat{\hat{\theta}}_\mu)/{\cal L}(\hat{\mu},\hat{\theta}))$,
where $\hat{\mu}$ and $\hat{\theta}$ are the values of the parameters that
maximise the likelihood function (with the constraint $0\leq \hat{\mu} \leq \mu$),
and $\hat{\hat{\theta}}_\mu$ are the values of the nuisance parameters that maximise
the likelihood function for a given value of $\mu$.
In the absence of any significant deviation from the background expectation,
$q_\mu$ is used in the CL$_\text{s}$ method~\cite{Junk:1999kv,Read:2002hq} to set an upper limit
on the signal production cross-section times branching ratio at the 95\% CL. For a given signal scenario,
values of the production cross-section (parameterised by $\mu$) yielding CL$_\text{s} < 0.05$,
where CL$_\text{s}$ is computed using the asymptotic approximation~\cite{Cowan:2010js},
are excluded at 95\% CL. For discovery,

@@

@@

\begin{equation}
E_{F}(n,\alpha) =  \sum \limits_{\frac{n-1}{5}\alpha < \Delta R(k,jet)< \frac{n}{5}\alpha} \ptSup{(k)} \Biggm/ \sum \limits_{\Delta R(k,jet)< \alpha} \ptSup{(k)}
\end{equation}
with $k$ running over the jet constituents and $\alpha=0.05$. We construct 5 variables $E_{F}(n,\alpha)$ with $n=[1,2,3,4,5]$ and use them as input to the BDT.
The $W$ tagging performance has significantly better performance due to the use of the energy-flow variables. We choose the working points for the analyses presented later with a top and $W$ tagging efficiencies of $\epsilon_S^{\text{top}}=60\%$ and $\epsilon_S^{\text{W}}=90\%$ corresponding respectively to a background rejection of $\epsilon_B^{\text{top}}=\epsilon_B^{\text{W}}=90\%$. These working points corresponds to a cut at 0.15 on the BDT value for both taggers. Independent samples have been generated for the training sample and are independent of the one used in the analysis.  More details can be found in Appendix~\ref{sec:app:mva}
